\documentclass[12pt, a4paper]{article}
\usepackage{fontspec}
\defaultfontfeatures{Ligatures={TeX},Renderer=Basic} 
\setmainfont[Ligatures={TeX,Historic}]{Times New Roman}
\usepackage[russian, english]{babel}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{array}
\usepackage{titlesec}
\usepackage{setspace}
\usepackage{fancybox,fancyhdr}
\usepackage{titlesec}
\usepackage{lastpage}
\usepackage{float}
\usepackage{etoolbox}
\usepackage[font=small]{caption}
\usepackage[sorting=none]{biblatex}
\usepackage[titles]{tocloft}
\usepackage[top=3.5cm,bottom=2.5cm,left=2.5cm,right=2.5cm,headheight=17pt,includehead,includefoot,heightrounded]{geometry} 
\usepackage{xeCJK}
\setCJKmainfont{SimSun}
\counterwithin{figure}{section}

\newcommand{\anonsection}[1]{\section*{#1}\addcontentsline{toc}{section}{#1}}
\bibliography{../bib/bibliography}

\begin{document}
	\begin{titlepage}
		\begin{center}
			\LARGE{\textbf{Dalian University of Technology Undergraduate Capstone Project (Thesis)}}
			~~~
			\\
			~~~
			\\
			~~~
			\\
			~~~
			\\
			~~~
			\\
			\Large{\textbf{Influence of vortex generators in a turbulent boundary layer on local friction and transport}}
			~~~
			\\
			~~~
			\\
			~~~
			\\
			~~~
			\\
			\begin{verse}
			\begin{minipage}{0.3\textwidth}
				Department:\\  
				Major:\\
				Name:\\                 
				Student Number:\\                
				Supervisor:\\          
				Review Teacher:\\
				Completion Date:\\
			\end{minipage}
			\hfill
			\begin{minipage}{0.6\textwidth}
				\underline{\hspace{1cm}DUT-BSU Joint Institute\hspace{1.9cm}}\\   
				\underline{\hspace{1cm}Engineering Mechanics\hspace{2.15cm}}\\  
				\underline{\hspace{1cm}Dima Shevelev\hspace{3.85cm}}\\   
				\underline{\hspace{1cm}1922241\hspace{5.15cm}}\\
				\underline{\hspace{1cm}PhD. Ass. Prof. Andrei Chorny\hspace{0.5cm}}\\ 
				\underline{\hspace{1cm}Prof. Zhuravkov Michael\hspace{2cm}}\\
				\underline{\hspace{1cm}2023-04-20\hspace{5.5cm}}\\  
			\end{minipage}
			\end{verse}
			~~~
			\\
			~~~
			\\
			~~~
			\\
			~~~
			\\
			\Large{大连理工大学}
			~~~
			\\
			Dalian University of Technology
		\end{center}  
	\end{titlepage}
	\newpage
	\pagestyle{fancy}
	\fancyhead[R]{Capstone Thesis}
	\fancyhead[L]{Dalian University of Technology}
	\fancyfoot[C]{-\thepage-}
	\begin{center}
		\textbf{原创性声明}
	\end{center}

	本人郑重声明：本人所呈交的毕业设计（论文），是在指导老师的指导下独立进行研究所取得的成果。毕业设计（论文）中凡引用他人已经发表或未发表的成果、数据、观点等，均已明确注明出处。除文中已经注明引用的内容外，不包含任何其他个人或集体已经发表或撰写过的科研成果。对本文的研究成果做出重要贡献的个人和集体，均已在文中以明确方式标明。
	\\\\
	本声明的法律责任由本人承担。
	~~~
	\\
	~~~
	\\
	~~~
	\\
	作者签名：\hspace{110pt}日  期：\\                 
	(Signed by the author)\hspace{40pt}(Date)
	\newpage
	\begin{center}
		\textbf{关于使用授权的声明}
	\end{center}
	本人在指导老师指导下所完成的毕业设计（论文）及相关的资料（包括图纸、试验记录、原始数据、实物照片、图片、录音带、设计手稿等），知识产权归属大连理工大学。本人完全了解大连理工大学有关保存、使用毕业设计（论文）的规定，本人授权大连理工大学可以将本毕业设计（论文）的全部或部分内容编入有关数据库进行检索，可以采用任何复制手段保存和汇编本毕业设计（论文）。如果发表相关成果，一定征得指导教师同意，且第一署名单位为大连理工大学。本人离校后使用毕业毕业设计（论文）或与该论文直接相关的学术论文或成果时，第一署名单位仍然为大连理工大学。
	~~~
	\\
	~~~
	\\
	~~~
	\\
	论文作者签名：\hspace{110pt}日  期：\\               
	(Signed by the author)\hspace{70pt}(Date)\\
	指导老师签名：\hspace{110pt}日  期：\\                
	(Signed by the instructor)\hspace{50pt}(Date)
	\newpage
	\tableofcontents
	\newpage
	\anonsection{Abstract}
	Turbulent boundary layers develop on the surfaces of many engineering structures: from heat exchange devices, elements of air-jet engines to aircraft airframes, ship hulls and large building structures. They determine both frictional resistance and heat transfer. The vortex structure of these layers opens up the possibility of changing it by influencing the process of vortex formation.
	
	One of the ways to control and reduce energy losses in a turbulent boundary layer is to use active and passive turbulence control methods, for example, installing transverse ribs (vortex generators) on the surface or introducing a heat flux into the walls. A deeper understanding of the features of the turbulent boundary layer can help reduce energy costs and improve the efficiency of various technologies.
	
	Theoretical methods for modeling and studying transport phenomena in the boundary layer can conditionally be classified into exact, asymptotic, numerical, and approximate methods. Approximate and numerical methods are more often used for mathematical modeling of transport phenomena and determining the efficiency of ongoing processes in industrial devices.
	
	The modern development of turbulence as a science is not possible without the use of powerful computers that implement various models and make it possible to identify their strengths and weaknesses. It is the computational experiment that today is the source of the development of turbulence models, which, in turn, are the basis for the creation of new computational tools.
	
	The purpose of this work is to study the effect of a vortex generator installed along the entire length of the channel on local friction and transfer. The ANSYS Fluent package was used for calculations and for post-processing of the received CFD Post data. The method of modeling large eddies was used as a method.\\
	
	\textbf{Keywords:} vortex generator, boundary layer, turbulence, large eddy simulation, local friction and transport, grid model, modeling, analysis.\\	
	\newpage
	\section{Theory of boundary layer and its modeling}
	\input{chp1.tex}
	\newpage
	\section{Modeling of the task}
	\input{chp2.tex}
	\newpage
	\section{Data analysis}
	\input{chp3.tex}
	\newpage
	\input{end.tex}
	\addcontentsline{toc}{section}{Conclusion}
	\newpage
	\printbibliography
	\addcontentsline{toc}{section}{References}
	\newpage
	\addcontentsline{toc}{section}{Acknowledgments}
	\begin{center}
		\Large\textbf{Acknowledgments}
	\end{center}
	\newpage
	\begin{center}
		\Large\textbf{Revision record}
	\end{center}
\end{document}